\documentclass[12pt,a4paper]{scrartcl}
\usepackage[english]{babel}
\usepackage{feynmf}
\usepackage{braket}
\usepackage{amssymb,amsmath}
\usepackage{dsfont}
\usepackage{rotating}
\usepackage{graphicx}
%\usepackage{gensymb}
\usepackage{epsfig}
\usepackage{subfig}
\usepackage{wrapfig}
\usepackage{nicefrac}
\usepackage{color}
\usepackage{float}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage{amssymb,amsmath}
\title{$\rho$admap to Analysis}
\author{Christopher Helmes}
\begin{document}
\maketitle
\section{Prerequisities}
\subsection{Real World}
In principal we want to analyse the mass $m_{\rho}$ and the decay width
$\Gamma_{\rho}$ of the $\rho$-resonance. For this we utilize in a first approach
a $2\times 2$ Correlation Matrix in the center of mass frame and two different
moving frames. The entries of the correlation matrix involve the two different
For each frame under consideration the analysis follows the same steps
operators specified in the paper by Feng, Jansen and Renner: 
\begin{align}
  &\mathcal{O}_{\pi\pi}(t) =
  \pi^+(\vec{P},t)\pi^-(0,t)-\pi^+(0,t)\pi^+(\vec{P},t) \\
  &\mathcal{O}_{\rho}(t) = \rho^0(\vec{P},t)
\end{align}

For each frame under consideration the analysis follows the same steps. The
scattering amplitude in inelastically interacting systems is given by the
relativistic Breit-Wigner formula:
\begin{displaymath}
  a_l = \frac{-\sqrt(s)\Gamma_R(s)}{s-M_R^2+i\sqrt{s}} 
\end{displaymath}
with the CM energy $E_{CM}^2 = s$ and the mass of the resonance $M_R$. The
relation between scattering amplitude and scattering phaseshift $\delta_l$
yields:
\begin{align}
  \tan \delta_l = \frac{\sqrt{s}\Gamma_R(s)}{M_R^2-s}
\end{align}
Taking into account p-wave scattering ($l=1$), the effective coupling
constant $g_{\rho\pi\pi}$, the $\rho$-mass, the $\pi$-mass $m_{\pi}$ and the
center of mass energy give rise to the effective range formula
\begin{displaymath}
  \tan \delta_1 = \frac{g^2_{\rho\pi\pi}}{6\pi}
  \frac{p^3}{E_{CM}(m^2_{\rho}-E^2_{CM})} \quad, \qquad p =
  \sqrt{\frac{E^2_{CM}}{4}-m^2_{\pi}}
\end{displaymath}

\subsection{Lattice}
\section{Analysis}
Given the contractions have been made the resulting Correlation functions
involving every combination of the operators $\mathcal{O}_{\pi\pi}$ and
$\mathcal{O}_{\rho}$ are combined in a bootstrap analysis to extract the two
energy-levels from the correlation matrix. In a first step the $N_C$
configurations are bootstrapped according to the following pattern:
View the (symmetrized) correlation functions as a 2d array in $n_c =
1,\dots,N_C$ and $t = 1,\dots, \nicefrac{T}{2}$, where $T$ is the lattice time
extent. One obtains $N_{BS}$ Bootstrapsamples of the $N_C$ correlation functions at
every value for $t$ as a sum over $N_C$ arbitrarily chosen values of $C(t)$ the
sample with $n_{BS} = 1$ is taken as the sum (average) of the original dataset.
In the end there exists a 2d array of size $N_{BS}\times \nicefrac{T}{2}$ 
A short illustration may clarify things.
%\begin{bmatrix}
%  
%\end{bmatrix}

On every bootstrap sample the correlation matrix $C_{ij}(t) =
\braket{O_i(t)O^{\dag}_j(0)}$ can be built. Cast into a generalized eigenvalue
problem this yields:

\begin{align}
  C(t)v_n(t,t_0) = \begin{pmatrix}
    \braket{\mathcal{O}_{\pi\pi}\mathcal{O}^{\dag}_{\pi\pi}}(t) &
    \braket{\mathcal{O}_{\pi\pi}\mathcal{O}^{\dag}_{\rho}}(t) \\
    \braket{\mathcal{O}_{\rho}\mathcal{O}^{\dag}_{\pi\pi}}(t) &
    \braket{\mathcal{O}_{\rho}\mathcal{O}^{\dag}_{\rho}}(t)
  \end{pmatrix} \begin{pmatrix} v_{n,1}(t,t_0) \\ v_{n,2}(t,t_0) \end{pmatrix} =
  \lambda_n(t,t_0) C(t_0) v_n(t,t_0)
\end{align}
The eigenvalues $\lambda_n$ are given by:
\begin{align}
  \lambda_n(t,t_0) = \exp[-E_n(t-t_0)]
\end{align}
corresponding to the energies of interest (in our case $n < 2$). To prevent
contamination stemming from states with $n > 2$ we use the correlation matrix
$R(t,t_R)$ composed of:
\begin{align}
  R(t,t_R)=C_{2\times 2}(t)C^{-1}_{2\times 2}(t_R)
\end{align}
In this approach the eigenvalues behave as
\begin{align}
  \tilde{\lambda}_n(t) = A_n \cosh\left[-E_n\left(t-\frac{T}{2}\right)\right]
\end{align}

The derivative method used in the case of $\pi\pi$-scattering to cancel out
contributions to the correlation matrix which are constant in $t$ is spoiled
here by the time dependence of these contributions. A general correlation
function can be written as:
\begin{align}
  \braket{\mathcal{O}_i \mathcal{O}^{\dag}_j}(t) &= \frac{1}{Z}
 \text{tr} \left[ \exp[-\hat{H}(T-t)]\mathcal{O}_i(0)\exp[-\hat{H}t]\mathcal{O}^{\dag}_j(0)
  \right] \\
  &= \sum_{m,n} V_{imn}V^{\dag}_{jmn}\exp \left[ -(E_m+E_n)\nicefrac{T}{2} \right]
  \cosh \left[ (E_m-E_n)(t-\nicefrac{T}{2}) \right] 
\end{align}

with the matrix elements $V_{imn}$
\begin{align}
  V_{imn} = \braket{m|\mathcal{O}_i(t)|n}
\end{align}

Taking $E_m > 0$ and $E_n > 0$ the thermally suppressed states also contribute
with a time dependant factor of the $\cosh$ and therefore influence the
Correlation functions. Because of the nonconstant contribution the derivative
method fails.

\subsection{Uncertainties}
The uncertainties in the approach proposed above are divided into statistical
and systematical ones. Statistical uncertainties can be assessed by the standard
deviation of the mean value on each bootstrap sample. The difference between the
sample means and the mean value obtained from the original data serves as an
estimator for the bias.\\
Systematic uncertainties can be inferred from a distribution of fit results
where each fit result is obtained using a varying fit range. The median of the
distribution of the values gives an estimate on the systematic error.

\end{document}

